The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-09 talk/vmil2012/paper.tex
don't use the footnote, they confuse google scholar and we have only one affiliation anyway

\authorinfo{David Schneider$^{a}$ \and Carl Friedrich Bolz$^a$}
           {$^a$Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {david.schneider@uni-duesseldorf.de \and cfbolz@gmx.de}

>>>>

\authorinfo{David Schneider \and Carl Friedrich Bolz}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany
           }
           {david.schneider@uni-duesseldorf.de \and cfbolz@gmx.de}
